\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/introduction.tex
paper: fix citation issues

% Solution
One common approach is to manually replace missing values using some sort of statistical or predictive model based on other values in the table and record.
This process is called \emph{imputation}.
In this paper, we present a new system, called \ProjectName{}, which is the designed to selectively apply imputation to a subset of records, on-the-fly, during query execution.  \emph{The key insight behind \ProjectName{} is that imputation
only needs to be performed on the data relevant to a particular query and
that this subset is generally much smaller than the entire database.}  
% Background
While traditional imputation methods work over the entire data set and replace all missing values, running a sophisticated imputation algorithm over a large data set can be very expensive -- out experiments show that even a relatively simple regression algorithm algorithms tables about XXX minutes to train and run
on a 600K row database;  prior work~\cite{AkandeEtAl} reports times of 45 minutes to impute missing values on a 1\% sample of an XXX row database.
\srm{Make numbers above consistent with experiments.}
A simpler approach might drop all rows with missing values, but not only can this introduce bias into the results, but this may result in discarding all of the data.
In contrast to existing systems~\cite{burgette2010multiple,akande2015empirical}, \ProjectName{} avoids imputing over the entire data set, as done with traditional methods. Specifically, \ProjectName{}
carefully plans the placement  imputation / row drop operations inside the query plan, resulting in a 
significant speedup in query execution while minimizing the number of dropped rows.  Also unlike previous work, the focus on of our work is not on the imputation algorithms themselves (we can employ almost any such algorithm), but rather on the  query planning involved in placement of imputation operations
in an optimal way into query plans.   Specifically, our optimization algorithms generate the Pareto-optimal frontier of plans that trade imputation cost for result quality.

>>>>

% Solution
One common approach is to manually replace missing values using some sort of statistical or predictive model based on other values in the table and record.
This process is called \emph{imputation}.
In this paper, we present a new system, called \ProjectName{}, which is the designed to selectively apply imputation to a subset of records, on-the-fly, during query execution.  \emph{The key insight behind \ProjectName{} is that imputation
only needs to be performed on the data relevant to a particular query and
that this subset is generally much smaller than the entire database.}  
% Background
While traditional imputation methods work over the entire data set and replace all missing values, running a sophisticated imputation algorithm over a large data set can be very expensive---our experiments show that even a relatively simple regression algorithm takes about XXX minutes to train and run
on a 600K row database; prior work~\cite{akande2015empirical} reports times of 45 minutes to impute missing values on a 1\% sample of an XXX row database.
\srm{Make numbers above consistent with experiments.}
A simpler approach might drop all rows with missing values, but not only can this introduce bias into the results, but this may result in discarding all of the data.
In contrast to existing systems~\cite{burgette2010multiple,akande2015empirical}, \ProjectName{} avoids imputing over the entire data set, as done with traditional methods. Specifically, \ProjectName{}
carefully plans the placement  imputation / row drop operations inside the query plan, resulting in a 
significant speedup in query execution while minimizing the number of dropped rows.  Also unlike previous work, the focus on of our work is not on the imputation algorithms themselves (we can employ almost any such algorithm), but rather on the  query planning involved in placement of imputation operations
in an optimal way into query plans.   Specifically, our optimization algorithms generate the Pareto-optimal frontier of plans that trade imputation cost for result quality.
